---
title: "R Notebook"
output: html_notebook
---
To update my master: 
1. git checkout master
2. git pull origin master
3. (then check back out working branch, such as temp)

To work with git on branch: 
1. git branch (if not on temp, create and check out temp branch)
2. *make changes*
3. *save*
4. git status
5. git add .
6. git commit -m "<commit details>"
7. git push origin temp
8. *go to firstofhername git page repo: https://github.com/thefirstofhername/tidytuesday/branches/yours
9. wait for commit to show up
10. select "new pull request"
11. verify able to merger, if no then fix merge conflicts
12. if yes, select "create pull request"
13. once verified, select "Merge pull request"
14. select "Confirm merge"
15. select "delete branch"

```{r}
# git push origin
# git pull upstream master
library(tidyverse)
```


```{r}
trains_raw <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-02-26/full_trains.csv")
small_trains <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-02-26/small_trains.csv") 

trains_raw
small_trains
```

```{r}
trains_canceled <- trains_raw %>% 
  group_by(departure_station) %>% 
  summarise(sum_of_canceled_trains = sum(num_of_canceled_trains)) %>% 
  top_n(wt = sum_of_canceled_trains, 20)
  #mutate(num_of_canceled_trains = sum(num_of_canceled_trains))
  #arrange(desc(num_of_canceled_trains)) %>% 
  #head(100)

g <- ggplot(trains_canceled, aes(x = reorder(departure_station, sum_of_canceled_trains), y = sum_of_canceled_trains)) +
  geom_bar(fill = '#001e93', stat = "identity") + #001e93 #ffffff #ef2637
  coord_flip() +
  labs(x = "Departure Station", y = " ", title = "French Train Stations with the Most Cancelations") +
  geom_text(aes(label = sum_of_canceled_trains), colour = '#ffffff', position = position_stack(vjust = .75))# +
  #theme(axis.text.x = element_blank(), 
        #panel.background = element_rect(fill = '#001e93'), 
        #axis.line = element_line(size = 0.5, linetype = "solid", colour = '#ef2637'),
        #panel.border = element_line(size = 0.5, colour = '#ef2637'),
        #panel.grid.major = element_line(size = 0.5, colour = '#ef2637'),
        #panel.grid.minor = element_line(size = 0.5, colour = '#ef2637'))
g
```

```{r}
trips_canceled <- trains_raw %>% 
  filter(year != 2018) %>% 
  mutate(trip_combinations = paste(departure_station, arrival_station, sep = " - ")) %>% 
  group_by(trip_combinations) %>% 
  summarise(sum_of_canceled_trains = sum(num_of_canceled_trains)) %>% 
  top_n(wt = sum_of_canceled_trains, 20)

g <- ggplot(trips_canceled, aes(x = reorder(trip_combinations, sum_of_canceled_trains), y = sum_of_canceled_trains)) +
  geom_bar(fill = '#ef2637', stat = "identity") +
  coord_flip() +
  labs(x = "Departure Station - Arrival Station", y = "", 
       title = "Most Commonly Canceled Trip Combinations", 
       subtitle = "Excluding year 2018 due to train workers strike") +
  geom_text(aes(label = sum_of_canceled_trains), colour = 'black', position = position_stack(vjust = .75)) +
  theme_minimal() +
  theme(axis.text.x = element_blank())
g
```


